---
title: "datathon_map"
author: "jmpark"
date: "2019년 3월 5일"
output: html_document
---

### Data Load
```{r,message=FALSE,warning=FALSE}
######## [LIBRARY] ########
library(readxl)
library(tidyverse)
library(ggplot2)
library(gridExtra)


######## [DATA] ########
datathon <- read_xlsx('C:\\Users\\jeong\\Desktop\\datathon.xlsx',sheet = 1)
country <- read_xlsx('C:\\Users\\jeong\\Desktop\\datathon.xlsx',sheet = 2)

```

### Data Preprocessing
```{r,message=FALSE,warning=FALSE}
######## [CODE] data of ages 0-4 (year: 2001-2015) ########
datathon2 <- datathon
## latest 15-year data (2003-2015)
myyear <- as.character(2003:2017)

## select rows that do not have any NA
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
mydata <- completeFun(datathon2,myyear)
mydata2 <- mydata[,-c(5:47,63)]

```


### Demographic Dividend
```{r,message=FALSE,warning=FALSE}
######## [DATA] data_all ########
## group data by year
data_all <- mydata2 %>% 
  gather(key = year, value = value,
         -`Country Name`,-`Country Code`,-`Indicator Code`,-`Indicator Name`)

######## [DATA] data_all2 / all_single / all_group ########
## classify data
data_all2 <- left_join(data_all,country %>% 
                         select(`Country Code`,Region))
## continental information O
Non_region <- data_all2 %>% 
  distinct(`Country Name`,`Country Code`,Region) %>% 
  filter(is.na(Region)) %>% select(`Country Name`)

## continental information X
region <- data_all2 %>% 
  distinct(`Country Name`,`Country Code`,Region) %>% 
  filter(!is.na(Region)) %>% select(`Country Name`)

all_single <- data_all2 %>% 
  filter(`Country Name` %in% region$`Country Name`)
all_group <- data_all2 %>% 
  filter(`Country Name` %in% Non_region$`Country Name`) %>% 
  select(-Region)

```


```{r,message=FALSE,warning=FALSE}
######## [DATA] demo ########
demo <- all_group %>% 
  filter(`Country Name` %in% c('Early-demographic dividend',
                               'Late-demographic dividend',
                               'Post-demographic dividend',
                               'Pre-demographic dividend'))

## rearrange levels
demo$`Country Name` <- factor(demo$`Country Name`,
                              levels = c('Pre-demographic dividend',
                                         'Early-demographic dividend',
                                         'Late-demographic dividend',
                                         'Post-demographic dividend'))


######## [DATA] demo_f / demo_m ########
demo_f <- demo %>% 
  filter(`Indicator Code` %in% c('SE.PRM.NENR.FE',
                                 'SE.SEC.NENR.FE'))
demo_m <- demo %>% 
  filter(`Indicator Code` %in% c('SE.PRM.NENR.MA',
                                 'SE.SEC.NENR.MA'))
ff <- demo_f %>% 
  select(`Country Name`,`Indicator Name`,year,value) %>% 
  mutate('gender'='Female')
mm <- demo_m %>% 
  select(`Country Name`,`Indicator Name`,year,value) %>% 
  mutate('gender'='Male')
tt <- rbind(ff,mm)

ggplot(tt,aes(year,value,
              group=interaction(`Indicator Name`,gender),
              color=interaction(`Indicator Name`,gender),
              linetype=interaction(`Indicator Name`,gender))) +
  geom_line(lwd=1) + theme_bw() +
  labs(y='(% net)') +
  theme(legend.position = 'bottom',
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_discrete(breaks = seq(2003,2017,by=3)) +
  scale_color_manual('',values = c('tomato','royalblue1','tomato','royalblue1'),
                     labels = c('Primary School enrollment, Female',
                                'Secondary School enrollment, Female',
                                'Primary School enrollment, Male',
                                'Secondary School enrollment, Male')) +
  scale_linetype_manual('',values = c(1,1,3,3),
                     labels = c('Primary School enrollment, Female',
                                'Secondary School enrollment, Female',
                                'Primary School enrollment, Male',
                                'Secondary School enrollment, Male')) +
  guides(color=guide_legend(nrow=2,byrow = T)) +
  facet_grid(~`Country Name`)

```

 It is clearly shown that as countries enter a more developed demographic period, the percentage of people engaging in education rises. This supports the findings of recent research that the demographic dividend is an education-triggered dividend.
 
 
### Variables related to the Demographic dividend
```{r,message=FALSE,warning=FALSE}
######## [DATA] demo_depend ########
demo_depend <- demo %>% 
  filter(`Indicator Code` %in% c('SP.POP.DPND',
                                 'SL.UEM.TOTL.FE.ZS',
                                 'SP.RUR.TOTL',
                                 'SH.IMM.IDPT',
                                 'SH.IMM.MEAS',
                                 'SH.IMM.POL3',
                                 'SH.DYN.MORT'))

myplot_fun <- function(mydata=data,mytitle=title,legend_pos='none'){
  p1 <- ggplot(mydata,
       aes(year,value,group=`Country Name`,color=`Country Name`)) +
  geom_line(lwd=1) + theme_bw() +
  labs(y='',title=mytitle) +
  theme(legend.position = legend_pos,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 8)) +
  scale_x_discrete(breaks = seq(2003,2017,by=3)) + 
  guides(color=guide_legend(nrow=1,byrow=TRUE)) +
  scale_color_manual('',values = 1:4)
  return(p1)
}

p11 <- myplot_fun(mydata = demo_depend %>% 
                    filter(`Indicator Code`=='SP.POP.DPND'),
                  mytitle = 'Age dependency ratio (% of working-age population)',
                  legend_pos = 'bottom')

p12 <- myplot_fun(mydata = demo_depend %>% 
                    filter(`Indicator Code`=='SL.UEM.TOTL.FE.ZS'),
                  mytitle = 'Unemployment, female (% of female labor force)')

p13 <- myplot_fun(mydata = demo_depend %>% 
                    filter(`Indicator Code`=='SP.RUR.TOTL'),
                  mytitle = 'Rural population')

p14 <- myplot_fun(mydata = demo_depend %>% 
                    filter(`Indicator Code`=='SH.IMM.IDPT'),
                  mytitle = 'Immunization, DPT (% of children ages 12-23 months)')

p15 <- myplot_fun(mydata = demo_depend %>% 
                    filter(`Indicator Code`=='SH.IMM.MEAS'),
                  mytitle = 'Immunization, measles (% of children ages 12-23 months)')

p16 <- myplot_fun(mydata = demo_depend %>% 
                    filter(`Indicator Code`=='SH.IMM.POL3'),
                  mytitle = 'Immunization, Pol3 (% of one-year-old children)')

p17 <- myplot_fun(mydata = demo_depend %>% 
                    filter(`Indicator Code`=='SH.DYN.MORT'),
                  mytitle = 'Mortality rate, under-5 (per 1,000)',
                  legend_pos = 'bottom')

## extract legend
## https://github.com/hadley/ggplot2/wiki/Share-a-legend-between-two-ggplot2-graphs
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(p11)

grid.arrange(arrangeGrob(p11 + theme(legend.position="none"),
                         p12,p13,p14,p15,p16,
                         nrow = 2),
             mylegend,
             heights=c(10,1))
```


```{r,message=FALSE,warning=FALSE}
p17

```

As countries develop they encounter a process called the demographic transition. In this phase birth rates and death rate both decrease as a country develops into an industrialized economic system. At the same time, as the population becomes more educated the death rate of children steadily decreases.
Mark the mortality rate of children on the map

```{r,message=FALSE,warning=FALSE}
library(ggmap)
library(ggplot2)
library(dplyr)
library(PBSmapping) # to clip polygons
require(ggthemes) # for theme_map, if desired

single <- all_single %>% filter(year==2017,`Indicator Code`=='SH.DYN.MORT')
country_name <- single %>% distinct(`Country Name`)

## define data (a simple dataset is constructed here
## for illustration purposes) and background map
countryData<-data.frame(region=as.character(single$`Country Name`), 
                        data=single$value)
nMap <- get_map(location = 'world',zoom=1,maptype="terrain",source="google")

## get country polygon data
mapdata <- map_data("world")
mapdata <- left_join(mapdata, countryData, by="region")

## find countries that do not match
country_name_map <- mapdata %>% filter(!is.na(data)) %>% distinct(region)
nomatch <- country_name %>% filter(!(`Country Name` %in% country_name_map$region))
single$`Country Name`[single$`Country Name`=='Antigua and Barbuda'] <- 'Antigua'
single$`Country Name`[single$`Country Name`=='Bahamas, The'] <- 'Bahamas'
single$`Country Name`[single$`Country Name`=='Brunei Darussalam'] <- 'Brunei'
single$`Country Name`[single$`Country Name`=='Cabo Verde'] <- ''
single$`Country Name`[single$`Country Name`=='Congo, Dem. Rep.'] <- 'Democratic Republic of the Congo'
single$`Country Name`[single$`Country Name`=='Congo, Rep.'] <- 'Republic of Congo'
single$`Country Name`[single$`Country Name`=="Cote d'Ivoire"] <- ''
single$`Country Name`[single$`Country Name`=='Egypt, Arab Rep.'] <- 'Egypt'
single$`Country Name`[single$`Country Name`=='Eswatini'] <- ''
single$`Country Name`[single$`Country Name`=='Gambia, The'] <- 'Gambia'
single$`Country Name`[single$`Country Name`=='Iran, Islamic Rep.'] <- 'Iran'
single$`Country Name`[single$`Country Name`=='Korea, Dem. People’s Rep.'] <- 'North Korea'
single$`Country Name`[single$`Country Name`=='Korea, Rep.'] <- 'South Korea'
single$`Country Name`[single$`Country Name`=='Kyrgyz Republic'] <- 'Kyrgyzstan'
single$`Country Name`[single$`Country Name`=='Lao PDR'] <- 'Laos'
single$`Country Name`[single$`Country Name`=='Macedonia, FYR'] <- 'Macedonia'
single$`Country Name`[single$`Country Name`=='Micronesia, Fed. Sts.'] <- ''
single$`Country Name`[single$`Country Name`=='Russian Federation'] <- 'Russia'
single$`Country Name`[single$`Country Name`=='Slovak Republic'] <- 'Slovakia'
single$`Country Name`[single$`Country Name`=='St. Kitts and Nevis'] <- 'Nevis'
single$`Country Name`[single$`Country Name`=='St. Lucia'] <- 'Saint Lucia'
single$`Country Name`[single$`Country Name`=='St. Vincent and the Grenadines'] <- 'Grenada'
single$`Country Name`[single$`Country Name`=='Syrian Arab Republic'] <- 'Syria'
single$`Country Name`[single$`Country Name`=='Trinidad and Tobago'] <- 'Trinidad'
single$`Country Name`[single$`Country Name`=='Tuvalu'] <- ''
single$`Country Name`[single$`Country Name`=='United Kingdom'] <- 'UK'
single$`Country Name`[single$`Country Name`=='United States'] <- 'USA'
single$`Country Name`[single$`Country Name`=='Venezuela, RB'] <- 'Venezuela'
single$`Country Name`[single$`Country Name`=='West Bank and Gaza'] <- ''
single$`Country Name`[single$`Country Name`=='Yemen, Rep.'] <- 'Yemen'

countryData<-data.frame(region=factor(single$`Country Name`),
                        data=single$value)
nMap <- get_map('world',zoom=1,maptype="terrain",source="google")
mapdata <- map_data("world")
mapdata <- left_join(mapdata, countryData, by="region")

## clip polygons to map
colnames(mapdata)[1:6] <- c("X","Y","PID","POS","region","subregion")

## plot map overlay
world_map <- map_data("world")
p <- ggplot() + coord_fixed()
base_world <- p + geom_polygon(data=world_map,
                               aes(x=long,
                                   y=lat,
                                   group=group))
real_plot <- base_world +
  geom_polygon(data=mapdata, aes(x=X, y=Y, group=PID, fill=data), alpha=1) +
  ggthemes::theme_map() +
  scale_fill_continuous(low = "moccasin",
                        high = "firebrick1", 
                        space = "Lab", guide = "colorbar") +
  ggtitle('Mortality rate, under-5 (per 1,000)',
          'Real')

real_plot

```


